Supplementary material for: \nA comparison of single-cell trajectory inference methods: towards more accurate and robust tools

### 2018-09-21 manuscript/supplementary.Rmd
Update supplementary RMD

---
title: "A comparison of single-cell trajectory inference methods: towards more accurate and robust tools"
output: 
  dynbenchmark::pdf_manuscript:
      render_change: FALSE
---

# Supplementary material

>>>>

---
title: "Supplementary material for: \nA comparison of single-cell trajectory inference methods: towards more accurate and robust tools"
output: 
  dynbenchmark::pdf_manuscript:
      render_change: FALSE
---
